\begin{thebibliography}{20} 
\bibitem{anand2024}Anand, A., Gupta, A., Yadav, N. \& Bajaj, S. A Comprehensive Survey of AI-Driven Advancements and Techniques in Automated Program Repair and Code Generation. {\em ArXiv Preprint ArXiv:2411.07586}. (2024)
\bibitem{alannsary2025}Alannsary, M. A Defect Classification Framework for AI-Based Software Systems (AI-ODC). {\em ArXiv Preprint ArXiv:2508.17900}. (2025)
\bibitem{yang2023}Yang, J., Wang, Y., Lou, Y., Wen, M. \& Zhang, L. A large-scale empirical review of patch correctness checking approaches. {\em Proceedings Of The 31st ACM Joint European Software Engineering Conference And Symposium On The Foundations Of Software Engineering}. pp. 1203-1215 (2023)
\bibitem{yang2025}Yang, B., Cai, Z., Liu, F., Le, B., Zhang, L., Bissyandé, T., Liu, Y. \& Tian, H. A Survey of LLM-based Automated Program Repair: Taxonomies, Design Paradigms, and Applications. {\em ArXiv Preprint ArXiv:2506.23749}. (2025)
\bibitem{liu2021}Liu, K., Li, L., Koyuncu, A., Kim, D., Liu, Z., Klein, J. \& Bissyandé, T. A critical review on the evaluation of automated program repair systems. {\em Journal Of Systems And Software}. \textbf{171} pp. 110817 (2021)
\bibitem{dikici2025}Dikici, S. \& Bilgin, T. Advancements in automated program repair: a comprehensive review. {\em Knowledge And Information Systems}. pp. 1-47 (2025)
\bibitem{jain2025}Jain, R. \& Purandare, R. Assessing Large Language Models in Comprehending and Verifying Concurrent Programs across Memory Models. {\em ArXiv Preprint ArXiv:2501.14326}. (2025)
\bibitem{liu2021}Liu, Z., Zhu, S., Qin, B., Chen, H. \& Song, L. Automatically detecting and fixing concurrency bugs in go software systems. {\em Proceedings Of The 26th ACM International Conference On Architectural Support For Programming Languages And Operating Systems}. pp. 616-629 (2021)
\bibitem{khoshnood2015}Khoshnood, S., Kusano, M. \& Wang, C. ConcBugAssist: constraint solving for diagnosis and repair of concurrency bugs. {\em Proceedings Of The 2015 International Symposium On Software Testing And Analysis}. pp. 165-176 (2015)
\bibitem{huang2016}Huang, J. \& Zhang, C. Debugging concurrent software: Advances and challenges. {\em Journal Of Computer Science And Technology}. \textbf{31}, 861-868 (2016)
\bibitem{aloufi2025}Aloufi, N. \& Aljuhani, A. Empirical Evaluation of Prompting Strategies for Python Syntax Error Detection with LLMs. {\em Applied Sciences}. \textbf{15}, 9223 (2025)
\bibitem{deng2015f}Deng, D., Jin, G., Kruijf, M., Li, A., Liblit, B., Lu, S., Qi, S., Ren, J., Sankaralingam, K., Song, L. \& Others Fixing, preventing, and recovering from concurrency bugs. {\em Science China Information Sciences}. \textbf{58}, 1-18 (2015)
\bibitem{upadhyay2023}Upadhyay, A., Laxmi, V. \& Naval, S. Navigating the Concurrency Landscape: A Survey of Race Condition Vulnerability Detectors. {\em ArXiv Preprint ArXiv:2312.14479}. (2023)
\bibitem{liyanage2025}Liyanage, S., Licorish, S., Wagner, M. \& MacDonell, S. On the need to perform comprehensive evaluations of automated program repair benchmarks: Sorald case study. {\em ArXiv Preprint ArXiv:2508.15135}. (2025)
\bibitem{yu2018}Yu, T., Wen, W., Han, X. \& Hayes, J. Conpredictor: Concurrency defect prediction in real-world applications. {\em IEEE Transactions On Software Engineering}. \textbf{45}, 558-575 (2018)
\bibitem{prenner2023}Prenner, J. \& Robbes, R. RunBugRun–An Executable Dataset for Automated Program Repair. {\em ArXiv Preprint ArXiv:2304.01102}. (2023)
\bibitem{chang2021}Chang, Y., Wu, H. \& Tsay, R. An Effective Parallel Program Debugging Approach Based on Timing Annotation. {\em ArXiv Preprint ArXiv:2109.04142}. (2021)
\bibitem{chen2025}Chen, Q., Li, D., Zhao, M., Wong, W. \& Li, H. Learning-based automated program repair: A systematic literature review. {\em Complex System Modeling And Simulation}. (2025)
\bibitem{abbaspour2016}Abbaspour Asadollah, S., Sundmark, D., Eldh, S., Hansson, H. \& Enoiu, E. A study of concurrency bugs in an open source software. {\em IFIP International Conference On Open Source Systems}. pp. 16-31 (2016)
\bibitem{kelk2013}Kelk, D., Jalbert, K. \& Bradbury, J. Automatically repairing concurrency bugs with ARC. {\em International Conference On Multicore Software Engineering, Performance, And Tools}. pp. 73-84 (2013)

\end{thebibliography}